
```{r, echo = FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 6,
  fig.path = "figs/",
  echo = TRUE
)

```



[![Travis-CI Build Status](https://travis-ci.org/reconhub/tracer.svg?branch=master)](https://travis-ci.org/reconhub/tracer)

[![Coverage Status](https://img.shields.io/codecov/c/github/reconhub/tracer/master.svg)](https://codecov.io/github/reconhub/tracer?branch=master)

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/tracer)](https://cran.r-project.org/package=tracer)


<br>
# Installing the package


To benefit from the latest features and bug fixes, install the development, *github* version of the package using:
```{r install2, eval=FALSE}
devtools::install_github("thibautjombart/tracer")
```

Note that this requires the package *devtools* installed.


<br>


# Contributors (by alphabetic order):
- [Thibaut Jombart](https://github.com/thibautjombart)


Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

**Maintainer:** Thibaut Jombart (thibautjombart@gmail.com)
